---
title: "Git File Visualizations"
output: html_notebook
---

```{r}
library(ggraph)
library(igraph)
library(tidyverse)
library(viridis)
```

```{r}
# We need a data frame giving a hierarchical structure. Let's consider the flare dataset:
edges <- flare$edges
vertices <- flare$vertices
mygraph <- graph_from_data_frame( edges, vertices=vertices )
```

```{r}
# Control the size of each circle: (use the size column of the vertices data frame)
ggraph(mygraph, layout = 'circlepack',)  + 
  geom_node_circle() +
  theme_void()
```

```{r}
# Libraries
library(packcircles)
library(ggplot2)
``` 

```{r}

# Create data
data <- data.frame(group=paste("Group", letters[1:20]), value=sample(seq(1,100),20)) 
 
```

```{r}

areas <- sample(c(4, 16, 64), 100, rep = TRUE, prob = c(60, 30, 10))
pack_fee <- circleProgressiveLayout(areas)

```

```{r}

# Generate the layout. This function return a dataframe with one line per bubble. 
# It gives its center (x and y) and its radius, proportional of the value
packing <- circleProgressiveLayout(mytree_group$size, sizetype='area')
 
# We can add these packing information to the initial data frame
data <- cbind(mytree_group, packing)


```
 
# Check that radius is proportional to value. We don't want a linear relationship, since it is the AREA that must be proportionnal to the value
# plot(data$radius, data$value)
 
# The next step is to go from one center + a radius to the coordinates of a circle that
# is drawn by a multitude of straight lines.

```{r}
dat.gg <- circleLayoutVertices(packing, npoints=50)
 
# Make the plot
ggplot() + 
  
  # Make the bubbles
  geom_polygon(data = dat.gg, aes(x, y, group = id, fill=as.factor(id)), colour = "black", alpha = 0.6) +
  
  # Add text in the center of each bubble + control its size
  geom_text(data = data, aes(x, y, size=size, label = path)) +
  scale_size_continuous(range = c(1,4)) +
  
  # General theme:
  theme_void() + 
  theme(legend.position="none") +
  coord_equal()

```

```{r}

# Circlepacker package
library(circlepackeR)
library(data.tree)
library(treemap)      
# devtools::install_github("jeromefroe/circlepackeR") # If needed

# create a nested data frame giving the info of a nested dataset:
data <- data.frame(
  root=rep("root", 15),
  group=c(rep("group A",5), rep("group B",5), rep("group C",5)), 
  subgroup= rep(letters[1:5], each=3),
  subsubgroup=rep(letters[1:3], 5),
  value=sample(seq(1:15), 15)
)

```

We'll try to recreate this format with the mytree_group frame, see what happens

```{r}

mytree_viz <- rename(mytree_group, root = path, group = path1, subgroup = path2, subsubgroup = path3)

```

```{r}

# Change the format. This use the data.tree library. This library needs a column that looks like root/group/subgroup/..., so I build it

# library(data.tree)
data$pathString <- paste("world", data$group, data$subgroup, data$subsubgroup, sep = "/")
population <- as.Node(data)

```

Make the node with our data

```{r}

repoviz <- as.Node(mytree_file)

```

```{r}
# Make the plot
#circlepackeR(population, size = "value")

# You can custom the minimum and maximum value of the color range.
p <- circlepackeR(repoviz, size = "size", color_min = "hsl(56,80%,80%)", color_max = "hsl(341,30%,40%)")

# save the widget
library(htmlwidgets)
saveWidget(p, file=paste0( getwd(), "/HtmlWidget/circular_packing_circlepackeR2.html"))

```

It works! Wow, that was unexpected. 



