---
title: "Creating file directory tibble"
output: html_notebook
---

We cloned the git repo into a temporary directory in the previous notebook. Now we are able to perform certain git commands and understand commits etc. But to explore the files we need to create a tibble out of the file directory.

For reasons unclear, I've named the directory of the repo "dendo_dir." Whatever. The value of this variable is the path to the cloned repo.

We use the fs library to create the first tibble of the directory, with path type and size.

```{r}
mytree <- dir_info(dendo_dir, recurse = TRUE) %>% select(path, type, size) %>% group_by(path)
```

We can now clean it up by removing all paths that we don't care about.

```{r}
 mytree <- mytree %>% mutate(path = str_remove(path, "/var/folders/n0/13y4pg1d20l4th9zbqpzjd640000gr/T/Rtmp1i69Wg/"))
```

We need to split the paths column into different columns so that we can perform visualizations. First let's take a look at how deep the directory tree goes by counting the number of slashes.

```{r}

mytree$paths <- str_count(mytree$path, "/")
max(mytree$paths)

```

It looks like the tree is only four directories deep at the deepest. So we separate the columns using the slash as a separator.

```{r}

mytree_file <- mytree

```


Let's see if there's an easier way to do this, by creating a file and path columns
```{r}

mytree_file <- mytree_file %>%
  separate(col = "path", c("path", "file"), "([/]*(?!.*[/]))", extra="merge", fill = 'right')

```

I kind of can't believe that worked. That's a bonkers RegEx, it's a hack that finds the last slash in the path by using a negative lookahead. To be honest, I don't understand why the .* is necessary, but it absolutely won't work without it. 

Anyway, we now have a path and file columns! That's great, except that in some rows the directory is in the wrong place. 

```{r}

mytree_group <- filter(mytree, type == "directory")

```

```{r}

mytree_file <- filter(mytree, type == "file")

```

```{r}

mytree_file$pathString <- mytree_file$path

```

```{r}

mytree_file <- separate(mytree_file, col = "path", c("root", "group", "subgroup", "subsubgroup", "file"), sep = "([/])", fill = "right")

```

```{r}

# Because we'll need a column with the full path (I think), we'll create it here before splitting everyting out

mytree_file$pathString <- mytree_file$path

```

Now we're free to split path

```{r}

mytree_group <- separate(mytree_group, col = "path", c("path", "path1", "path2", "path3"), sep = "([/])", fill = "right")

```


And now we have to rearrange the data so that the columns make sense

```{r}

mytree_group2 <- mytree_group %>%
  select(starts_with("path")) %>%
  mutate(v=c(v[!is.na(v)], rep(NA, length(v) - length(v[!is.na(v)]))))

```


