---
title: "R Notebook"
output: html_notebook
---

Install the library for part 1 and 2

```{r}
library(tidyverse)
library(glue)
library(stringr)
library(forcats)
```


Let's defgine a git repo

```{r}
repo_url <- "https://github.com/tidyverse/ggplot2.git"
```

And where are we going to put this fucker?

```{r}
clone_dir <- file.path(tempdir(), "git_repo")
```

Link them

```{r}
clone_cmd <- glue("git clone {repo_url} {clone_dir}")
```

```{r}
system(clone_cmd)
```

Let's see what we got 

```{r}
list.files(clone_dir)
```

Let's fuck around a bit

```{r}
system(glue('git -C {clone_dir} log -3'))
```

Let's try that gain, making it pretty

```{r}

log_format_options <- c(datetime = "cd", commit = "h", parents = "p", author = "an", subject = "s")
option_delim <- "\t"
log_format   <- glue("%{log_format_options}") %>% glue_collapse(option_delim)
log_options  <- glue('--pretty=format:"{log_format}" --date=format:"%Y-%m-%d %H:%M"')
log_cmd      <- glue('git -C {clone_dir} log {log_options}')
log_cmd
```


```{r}
system(glue('{log_cmd} -3'))
```

```{r}
history_logs <- system(log_cmd, intern = TRUE) %>% 
  str_split_fixed(option_delim, length(log_format_options)) %>% 
  as_tibble(.name_repair = ("minimal")) %>% 
  setNames(names(log_format_options))

history_logs
```

Check the parents column for space-separated strings, which can happen as the result of a merge. Change the parent column into a list-column of character vectors to handle this 

```{r}
history_logs <- history_logs %>% 
  mutate(parents = str_split(parents, " "))

history_logs

```

```{r}
history_logs <- history_logs %>% 
  mutate(datetime = as.numeric(datetime))

history_logs

```


Now we assign branch numbers to commits

Start with NA

```{r}
history_logs <- history_logs %>% mutate(branch = NA_integer_)
```

Finally, be sure to assign branch numbers to commits. There’s surely a better way to do this, but here’s one (very untidy) method:

```{r}
free_col <- rep(TRUE, 1000)

for (i in seq_len(nrow(history_logs) - 1)) { # - 1 to ignore root
  # Check current branch col and assign open col if NA
  branch <- history_logs$branch[i]

  if (is.na(branch)) {
    branch <- which.max(free_col)
    free_col[branch] <- FALSE
    history_logs$branch[i] <- branch
  }

  # Go through parents
  parents <- history_logs$parents[[i]]

  for (p in parents) {
    parent_col <- history_logs$branch[history_logs$commit == p]

    # If col is missing, assign it to same branch (if first parent) or new
    # branch (if other)
    if (is.na(parent_col)) {
      parent_col <- if_else(p == parents[1], branch, which.max(free_col))

    # If NOT missing this means a split has occurred. Assign parent the lowest
    # and re-open both cols (parent closed at the end)
    } else {
      free_col[c(branch, parent_col)] <- TRUE
      parent_col <- min(branch, parent_col)

    }

    # Close parent col and assign
    free_col[parent_col] <- FALSE
    history_logs$branch[history_logs$commit == p] <- parent_col
  }
}

history_logs

```

Now that we have the tidy git log, let's do some analysis

```{r}
history_logs %>% 
  count(author, sort = TRUE)
```

```{r}
history_logs <- history_logs %>% 
  mutate(author = case_when(
    str_detect(tolower(author), "hadley") ~ "Hadley Wickham",
    str_detect(tolower(author), "kohske takahashi") ~ "Kohske Takahashi",
    TRUE ~ str_to_title(author)
  ))

```


```{r}
history_logs %>% 
  count(author) %>% 
  top_n(10, n) %>% 
  mutate(author = fct_reorder(author, n)) %>% 
  ggplot(aes(author, n)) +
    geom_col(aes(fill = n), show.legend = FALSE) +
    coord_flip() +
    theme_minimal() +
    ggtitle("ggplot2 authors with most commits") +
    labs(x = NULL, y = "Number of commits", caption = "Post by @drsimonj")

```

Install the library for part 3

```{r}
# Part 3
library(tidygraph)
library(ggraph)
library(tidytext)
```

```{r}
history_logs <- history_logs %>%
  datetime <- as.numeric(datetime)
```

```{r}
# Convert commit to a factor (for ordering nodes)
history_logs <- history_logs %>% 
  mutate(commit = factor(commit))
```

```{r}
# Nodes are the commits (keeping relevant info)
nodes <- history_logs %>% 
  select(-parents) %>% 
  arrange(commit)
```

```{r}
# Edges are connections between commits and their parents
edges <- history_logs %>% 
  select(commit, parents) %>% 
  unnest(parents) %>% 
  mutate(parents = factor(parents, levels = levels(commit))) %>% 
  transmute(from = as.integer(parents), to = as.integer(commit)) %>% 
  drop_na()
```

```{r}
# Create tidy directed graph object
git_graph <- tbl_graph(nodes = nodes, edges = edges, directed = TRUE)
```
```{r}
git_graph
```

```{r}
git_graph(datetime)
```


```{r}
git_graph %>% 
  ggraph(layout = "nicely") +
    geom_edge_link(alpha = .1) +
    geom_node_point(aes(color = factor(branch)), alpha = .3) +
    theme_graph() +
    theme(legend.position = "none")
#> Using `nicely` as default layout
```


```{r}
ggraph_git <- . %>%
  datetime <- as.numeric(datetime)
```

  # Set node x,y coordinates
  activate(nodes) %>% 
  mutate(x = datetime, y = branch) %>%
```
```{r}
x
```


```{r}
git_graph
```

```{r}
ggraph_git <- . %>%
  # Plot with correct layout
  create_layout(layout = as_tibble(activate(., nodes))) %>% 
  {ggraph(.) + theme_graph()}
```

```{r}
git_graph %>% 
  activate(nodes) %>% 
  filter(datetime > "2015-11-01", datetime < "2016-08-01") %>% 
  ggraph_git() +
    geom_edge_link(alpha = .1) +
    geom_node_point(aes(color = factor(branch)), alpha = .3) +
    theme(legend.position = "none") +
    ggtitle("Git history of ggplot2",
            subtitle = "2015-11 to 2016-08")
```

```{r}
git_graph %>% 
  ggraph_git() +
    geom_edge_link(alpha = .1) +
    geom_node_point(aes(color = factor(branch)), alpha = .3) +
    theme(legend.position = "none") +
    ggtitle("Commit history of ggplot2")
```


