---
title: "R Notebook"
output: html_notebook
---


```{r}
# install.packages("cloc", repos = c("https://cinc.rud.is", "https://cloud.r-project.org/"))
```


```{r}

library(cloc)

cloc("https://raw.githubusercontent.com/tidyverse/dplyr/master/R/group-by.r")

```


```{r}

files <- cloc_by_file("~/sites/generalanalytics.io")

```



```{r}

files

```


```{r}

library(dplyr)
library(textshape)
library(lexicon)
library(textclean)

```

```{r}
#We clean up the filename to get rid of shit

files$filename <- gsub("/Users/aperture/sites/generalanalytics.io/", "", files$filename)


```


```{r}
files
```


```{r}
#The parser below needs a column called pathString

files <- rename(files, pathString = filename)

```

This function creates a dataframe with the path split into various columns  

```{r}

library(data.tree); library(plyr); library(purrr)

```

```{r}
split <- lapply(strsplit(files$pathString, "/"), function(z) as.data.frame(t(z)))
```

```{r}
# This is a super interesting function. It takes the bonkers list from above and creates separate rows for each element

split <- rbind.fill(split)
```

```{r}
# We need to create a pathstring as a key to merge the two dataframes together

# The apply function takes arguments: split is the dataframe, 1 is to execute apply over rows (2 would be columns), and then the function we want to apply to each row. The paste() concatenates ("link things together in a chain"), collapse provides the separator, 

split$pathString <- apply(split, 1, function(x) paste(trimws(na.omit(x)), collapse="/"))
# (mytree <- data.tree::as.Node(x))
```

```{r}
#Here we merge the two dataframes together using pathString as a key

merged <- merge(files, split, by = "pathString")

```

## Here we created a nested dataframe, with a nested column of the path variables. This in prep to create a Json

```{r}

library(tidyr)
library(dplyr)
library(purrr)

nested <- split %>%
           nest(path = c(V1, V2, V3, V4, V5, V6, V7, V8, V9, V10))

```


## Next we create a json using the as.Node function

```{r}
library(data.tree)

node <- as.Node(nested)

```

```{r}

print(node, "loc", "language")

```

And we can build the nested circle, something I've been working on for so long

```{r}
library(circlepackeR) 

circlepackeR(node, size = "loc", color_min = "hsl(56,80%,80%)", color_max = "hsl(341,30%,40%)")

```




```{r}
library(fs)

filez <- dir_tree(path="~/sites/generalanalytics.io", recurse = TRUE)
```



```{r}

filezz <- as_tibble(as.list(filez))

```

```{r}
filezz
```



```{r}
mytree
```




```{r}
# Circlepacker package
library(circlepackeR)         
# devtools::install_github("jeromefroe/circlepackeR") # If needed
```
# create a nested data frame giving the info of a nested dataset:
#data <- data.frame(
#  root=rep("root", 15),
#  group=c(rep("group A",5), rep("group B",5), rep("group C",5)), 
#  subgroup= rep(letters[1:5], each=3),
#  subsubgroup=rep(letters[1:3], 5),
#  value=sample(seq(1:15), 15)
#)

```{r}
# Change the format. This use the data.tree library. This library needs a column that looks like root/group/subgroup/..., so I build it

library(data.tree)
tree <- as.Node(files)

```

# Make the plot
#circlepackeR(population, size = "value")

# You can custom the minimum and maximum value of the color range.
p <- circlepackeR(population, size = "value", color_min = "hsl(56,80%,80%)", color_max = "hsl(341,30%,40%)")

# save the widget
# library(htmlwidgets)
# saveWidget(p, file=paste0( getwd(), "/HtmlWidget/circular_packing_circlepackeR2.html"))



```{r}
# Circlepacker package
library(circlepackeR)         
# devtools::install_github("jeromefroe/circlepackeR") # If needed

# create a nested data frame giving the info of a nested dataset:
data <- data.frame(
  root=rep("root", 15),
  group=c(rep("group A",5), rep("group B",5), rep("group C",5)), 
  subgroup= rep(letters[1:5], each=3),
  subsubgroup=rep(letters[1:3], 5),
  value=sample(seq(1:15), 15)
)

# Change the format. This use the data.tree library. This library needs a column that looks like root/group/subgroup/..., so I build it
library(data.tree)
data$pathString <- paste("world", data$group, data$subgroup, data$subsubgroup, sep = "/")
population <- as.Node(data)

# Make the plot
#circlepackeR(population, size = "value")

# You can custom the minimum and maximum value of the color range.
p <- circlepackeR(population, size = "value", color_min = "hsl(56,80%,80%)", color_max = "hsl(341,30%,40%)")

# save the widget
# library(htmlwidgets)
# saveWidget(p, file=paste0( getwd(), "/HtmlWidget/circular_packing_circlepackeR2.html"))

```

```{r}
filez

```

```{r}

rename(files, pathString = filename)

```

```
```{r}
files
```

